Contribution Title\thanks{Supported by organization x.}

### 2019-10-24 paper/paper.tex
Minor

This section briefly explains the notations used in this paper.
%
Given a context-free grammar $G$, we write $L(G)$ to denote the
set of all words recognized by $G$.
%
The standard definition of ambiguity states that a word
$w \in L(G)$ is ambiguous if there are two distinct leftmost
derivations of that word.
%
An automata is a 5-tuple $(Q,\T,\delta,q_0,F)$, where $Q$ is a
finite set of states; $\T$ a finite set of terminals; $\delta$ a
transition function from $Q \times \T$ to finite subsets of $Q$
(or single states of $Q$ for a deterministic automaton);
$q_0 \in Q$ an initial state; and $F \subseteq Q$ a set of final
states.
%
A pushdown automata further adds a set of stack symbols $\Gamma$
and equips the transition function $\delta$ with information on
which symbols are pushed, popped or just read from the stack.

Appendix~\ref{app:prel} contains a more detailed
description of the preliminaries (for reviewers).

@@

\appendix

>>>>

This section briefly explains the notations used in this paper.
Appendix~\ref{app:prel} contains a more detailed description of
the preliminaries (for reviewers).

\paragraph{Grammars}
Given a context-free grammar $G$, we write $L(G)$ to denote the
set of all words recognized by $G$.
%
The standard definition of ambiguity states that a word
$w \in L(G)$ is ambiguous if there are two distinct leftmost
derivations of that word.

\paragraph{Automata}
An automata is a 5-tuple $(Q,\T,\delta,q_0,F)$, where $Q$ is a
finite set of states; $\T$ a finite set of terminals; $\delta$ a
transition function from $Q \times \T$ to finite subsets of $Q$
(or single states of $Q$ for a deterministic automaton);
$q_0 \in Q$ an initial state; and $F \subseteq Q$ a set of final
states.
%
A pushdown automata further adds a set of stack symbols $\Gamma$
and equips the transition function $\delta$ with information on
which symbols are pushed, popped or just read from the stack.

@@

\pagebreak
\appendix
